Synpotic Soil Characterization

### 2024-08-20 3-reports/manuscript_figures.Rmd
update rmd

```{r scaled_gg2_split, fig.height = 16, fig.width = 16}
data_scaled_NEW %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
  facet_wrap( ~ name + region)+
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme_kp()+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())
```

@@

Version 1 - one region only

```{r analytesx, fig.height = 4, fig.width = 4}

data_combined_wide %>% 
  filter(region == "CB") %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  geom_text(data = tibble(x = c("upland", "transition", "wc"),
                          label = c("B", "A", "B")),
            aes(x = x, y = 800, label = label), size = 5)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")

data_combined_wide %>% 
    filter(region == "WLE") %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = P))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  geom_text(data = tibble(x = c("upland", "transition", "wc"),
                          label = c("B", "A", "B")),
            aes(x = x, y = 450, label = label), size = 5)+
  labs(x = "",
       y = "Extractable P, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")

Version 2 - both regions

>>>>

```{r scaled_gg2_split, fig.height = 16, fig.width = 18}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

data_scaled_NEW %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
#  facet_wrap( ~ name)+
  facet_nested_wrap(~ name + region, ncol = 8,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme_kp()+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())
```

@@
